Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-19 writeup/gz_hubble_data.tex
General feedback from RJS. Addresses #126.

The GZH classifications include 288 unique galaxies originally generated from
SDSS imaging and processed with the \ferengi{} code. The selection spanned a
variety of galaxy morphologies (as selected by GZ2 classifications) and
$r^\prime$-band surface brightnesses, and also spanned the redshift range of
SDSS targets that maximize the coverage of parameter space.

@@

The primary purpose of the GZH catalog is to provide a reliable method of
selecting galaxies of a desired morphological type.  This section provides
instructions for creating such samples using the vote fractions corresponding
to the tasks shown in Figure~\ref{fig:decisiontree}. More conservative cuts can
be applied to create pure, but not necessarily complete, samples. These are
useful for selecting galaxies exhibiting unique morphologies for individual
case studies.  Looser cuts can be applied to obtain samples with a higher level
of completeness, (but with a potential decrease on the overall purity). We
stress that the details of any selection process will vary based on the
particular science case.

>>>>

The GZH classifications include 288 unique galaxies originally generated from
SDSS imaging and processed with the \ferengi{} code. The selection spanned a
variety of galaxy morphologies (as selected by GZ2 classifications) and
$r^\prime$-band surface brightnesses, and also spanned the redshift range of
SDSS targets that maximize the coverage of parameter space
(Figure~\ref{fig:sb_redshift}).

@@

The primary purpose of the GZH catalog is to provide a reliable method of
selecting galaxies of a desired morphological type.  This section provides
instructions for creating such pure samples using the vote fractions
corresponding to the tasks shown in Figure~\ref{fig:decisiontree}
\citep[eg,][]{mas11c,che15,gal15}. Increasing the levels of the thresholds can
create purer, but not necessarily complete, morphologically-selected samples.
These are useful for selecting galaxies of rare or unique types that merit
individual study.  Looser cuts can be applied to obtain samples with a higher
level of completeness, although the rate of false positives must be closely
monitored.  We stress that the details of any selection process will vary based
on the particular science case; for example, \citet{bam09,ski09,sme15} demonstrate
the advantages of using the vote fractions directly as weights rather than
applying discrete thresholds.
